Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 ieee_paper.tex
minor

%\todo{Add few sentence with discretization. Check Erik}
In discrete form, Equation (\ref{eq:Q}) takes the form
$$
  y^{i,j} = A^i x^j 
$$
where $j$ ranges over the number of source vectors, $i$ ranges of the number of derivative
matrices and there are $i*j$ output vectors $y$.

% GORDON I WOULD ELIMINATE BELOW AND END HERE.

%**** PUT ELSEWHERE OR ELIMINATE? ****
%
%When solving a one dimensional system of PDEs, one might require an
%$x$ derivative of multiple functions. For example, the Euler equations
%require the $x$ derivative of the three components of velocity and
%pressure. In this case, there are $n_v=4$ vectors $x^k$,
%$k=0,\cdots,3$.
%
%Thus for each vector element $y_i$, we compute $y_i = \sum_j A_{ij}
%x_j$. If $A_i$ is row $i$ of $A$, $y_i$ is simply the dot product $A_i
%x$. The next level of generality is to consider $n_v$ vectors $x^k$,
%$k=0,\cdots,n_v-1$. Whatever the spmv implementation, one achieves
%improved performance if the matrix formed from the columns $x^k$ are
%stored in row major order. Thus, $x^0_0,x^1_0,\cdots,x^{n_v-1}_0$, are
%stored in consecutive memory location. The random access of the
%elements of $x$ is thus reduced. Maximum efficiency is achieved when
%$n_v=16$ floats or $8$ doubles, given that cache lines take 64
%bytes. We will benchmark this case, labeled $Svn$, where $n$ refers to
%the number of vectors (Iv4 uses four vectors). The $S$ refers to singe
%precision. A double precision run is labelled $Dvn$.
%
%Alternatively, when solving a PDE, one might require derivatives of a
%given scalar function with respect to coordinate directions $x$, $y$,
%$z$. Second order operators of often required, such as a second
%derivative with respect to $x$ or a Laplacian operator. In the RBFFD
%formulation, on can compute different derivatives using the same
%stencil, but with different weights. In other words, the adjacency
%matrix that corresponds to $A$ remains constant, but the matrix
%elements of $A$ change with the particular derivative.  In this case,
%label with a superscript $l$ the particular matrix $A^k$. Since the
%adjacency matrix is assumed invariant, there is only need for a single
%matrix \ttt{C{ij}}. In Ellpack format, each row is of constant size
%(the number of nonzeros per row of $A$. $C_{ij}$ is the column number
%that locates the $j^{th}$ nonzero in row $i$ of $A$.
%
%
%\todo{Must rewrite the above to make it more focused on the
% application. Remove the architectural/implementation details such as
%  using ELLPACK. Let's focus on on why this computation is important
%  and how does the 16 multiplication appears in the equations.}

@@

  \caption{Matrix of the computation.}
  \label{fig:mat_struct}
\end{figure}

@@

  \caption{Ratio of flops to bytes in single precision:  
    \ref{fig:ratio_best} best case; \ref{fig:ratio_worst} worst case when $cl=64$ 
    ; and \ref{fig:ratio_worst_nocache} worst case neglecting that the
    memory transfers are with a grenularity of one cache line (equivalent to $cl = 1$)}
  \label{fig:ratio_bytes_flops}
\end{figure*}

@@

\begin{figure}
  \centering 
  \includegraphics[width=.9\linewidth]{figures/gflops_peak.pdf}\label{fig:gflops-peak-perf}
  \caption{Estimation of the maximum achievable performance using a
    device with a memory to computational units of 150~GB/s when
    varying the number of vectors and matrices.\todo{yabel=Peak Performance (Gflop/s)}\todo{no xlabel}}
  \label{fig:perf_predict}
\end{figure}

>>>>

%\todo{Add few sentence with discretization. Check Erik}
In discrete form, Equation (\ref{eq:Q}) takes the form
$$
  y^{i,j} = A^i x^j 
$$ where $j$ ranges over the number of source vectors, $i$ ranges of
  the number of derivative matrices and there are $i*j$ output vectors
  $y$ (graphically shown in Figure~\ref{fig:struct_comp}).

@@

  \caption{Structure of the computation.}
  \label{fig:struct_comp}
\end{figure}

@@

  \caption{Ratio of flops to bytes in single precision:  
    \ref{fig:ratio_best} best case; \ref{fig:ratio_worst} worst case when $cl=64$ 
    ; and \ref{fig:ratio_worst_nocache} worst case neglecting that the
    memory transfers are with a granularity of one cache line (equivalent to $cl = 1$)}
  \label{fig:ratio_bytes_flops}
\end{figure*}

@@

\begin{figure}
  \centering 
  \includegraphics[width=.9\linewidth]{figures/gflops_peak.pdf}\label{fig:gflops-peak-perf}
  \caption{Estimation of the maximum achievable performance using a
    device with a bandwidth from memory to computational units of 150~GB/s when
    varying the number of vectors and matrices.\todo{yabel=Peak Performance (Gflop/s)}\todo{no xlabel}}
  \label{fig:perf_predict}
\end{figure}
